---
output:
   knitrBootstrap::bootstrap_document:
    title: "Bootstrap report"
    theme: spacelab
    highlight: sunburst
    theme.chooser: TRUE
    highlight.chooser: FALSE
---


Example Elements with KnitrBootStrap
===============



# Introduction

<div class='jumbotron'>
R has some great packages for generating reports. Here are some neat examples of what you can do with the KnitrBootstrap package and rmarkdown
</div>

The following packages are required:

* knitrBootstrap
* shiny
* rCharts
* googleVis
* data.table
* fifer


# Simple Table 

```{r, echo=T, warning=FALSE, message=FALSE}
library(knitr)
d=head(mtcars)
kable(d)
```
 
 
# A Fancier HTML Table

This table will sort dynamically if the columns are clicked. Plug any data frame into it.

```{r somdivid, echo=T,results='asis', message=F,warnings=FALSE, tidy=FALSE}
library(googleVis)
op <- options(gvis.plot.tag='chart')
df=mtcars
plot(gvisTable(df,options=list(page='enable')))

```
 


# Summary Demographics

Summarized variables into demographic information. Useful for providing high-level stats.

You will require the fifer packages and a  manifest file for this example below

```{r , echo=T, warning=FALSE, message=FALSE ,warning=FALSE}
library(fifer)
set.seed(1)
n <- 50
df <- data.frame(trt=sample(0:1, 2*n, replace=TRUE), x1=runif(2*n), x2=rnorm(2*n),
   x3=sample(c("a", "b", "c"), 2*n, replace=TRUE))
knitr::kable(demographics(trt~x1+x2+x3, data=df))
```

# Second section

```{r , echo=FALSE, warning=FALSE, message=FALSE}
boxplot(mtcars$mpg)
```

***************

# The Tabbed section 

## Quarterly Results {.tabset .tabset-pills }

### By Product

```{r , echo=FALSE, warning=FALSE, message=FALSE}
boxplot(mtcars$cyl)
```

### By Region

This be the irirs 

```{r , echo=FALSE, warning=FALSE, message=FALSE}
boxplot(iris$Sepal.Length)
```


# The Next section

```{r,echo=FALSE,warning=FALSE,message=FALSE }
library(shiny)
tags$span(class="label-info label","232423432")

```
 
# googleVis Example

A comnbined plot and table from googleVis


```{r ComboExample, echo=FALSE,results='asis', message=F,warnings=FALSE, tidy=FALSE}
library(googleVis)
op <- options(gvis.plot.tag='chart')

#plot(gvisTable(mtcars))
Geo <- gvisGeoChart(Exports, locationvar='Country', colorvar='Profit', 
                    options=list(height=300, width=350)) 
Tbl <- gvisTable(Exports, options=list(height=300, width=200))
plot(gvisMerge(Geo, Tbl, horizontal=TRUE))
```
 

# Pie chart

More googleVis examples. These all require  an internet connection

```{r piechart, echo=FALSE,results='asis', message=F,warnings=FALSE, tidy=FALSE}
library(googleVis)
op <- options(gvis.plot.tag='chart')
Pie2 <- gvisPieChart(CityPopularity, options=list(
                    slices="{4: {offset: 0.2}, 0: {offset: 0.3}}",
                    title='City popularity',
                    legend='none',
                    pieSliceText='label',
                    pieHole=0.5))
plot(Pie2)
```
 
# Tabset panel from Shiny

```{r sometabs, echo=FALSE,results='asis', message=FALSE,warnings=FALSE, tidy=FALSE}
library(shiny)
nTabs = 4
some_data <- tags$p("Hellow World ")
createTabs <- function(tabNum, content) {
      tabPanel(title = paste("Map", tabNum, sep=" "), 
           content
      )
}
mTabs <- lapply(0:nTabs, createTabs, some_data)
do.call(tabsetPanel, mTabs)
```


#Formatting {.tabset .tabset-pills }

## KnitrBootsrap Usage
 
Change the YAML front matter to the following below for KnitrBootstrap
<pre>
---
  output:
  knitrBootstrap::bootstrap_document:
  title: "Bootstrap report"
  theme: spacelab
  highlight: sunburst
  theme.chooser: TRUE
  highlight.chooser: FALSE
  #custom.header: "header.html"
  
  
---
</pre>

## Regular Knitr

Change the YAML front matter to the following below for Knitr
<pre>

---
title: "Regular Knitr"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
      
      
---

</pre>



#Author

Zayed I Alberyn, Dec 2016  [zayed@novocraft.com]





# The END 

